```{r loadPackagesAndData, include=FALSE}
library(tidyverse)
simPar <- read.csv(here::here("data", "manProcScenarios",
                        "fraserMPInputs_varyAllocationVaryMixHCR.csv"),
                   stringsAsFactors = F)
cuPar <- read.csv(here::here("data/summOnlyCUPars.csv"), stringsAsFactors = F)
srDat <- read.csv(here::here("data/fraserRecDatTrim.csv"), stringsAsFactors = F)
catchDat <- read.csv(here::here("data/fraserCatchDatTrim.csv"), 
                     stringsAsFactors = F)

stks <- unique(cuPar$stk)
d <- srDat %>% 
  filter(stk %in% stks,
         !is.na(rec2)) %>% 
  select(stk, yr) %>% 
  group_by(stk) %>% 
  summarise(min = min(yr), 
            max = max(yr))
maxY <- min(d$max)
minY <- max(d$min)
diff <- maxY - minY
```

# 2. METHODS 

Closed-loop simulations can be used to evaluate trade-offs among objectives of different management frameworks by simultaneously modeling biological populations and the fisheries that harvest them [@Punt2016]. Typically closed-loop simulations contain two main components--an operating model and a management procedure. The operating model represents system attributes largely beyond the control of managers, such as stock-recruit dynamics and deviations between target and realized catches. Conversely, the management procedure represents dimensions of the fishery that are under anthropogenic control, for example target harvest rates and methods for assessing status. Closed-loop simulations can be used to evaluate the performance of different management procedures by comparing alternative harvest control rules [@Cooke1999; @Holt2008; @Collie2012] or assessment frameworks [@KHolt2011; @PeacockPress]. Similarly, different operating models can be used to determine whether a given management procedure is resilient to uncertain ecological conditions, such as changes in natural mortality [@Holt2010; @Forrest2018; @Freshwater2019]. 

Our analysis involved manipulations to both of these components. Briefly, we included multiple management procedures, representing various degrees of stock-selectivity, that altered the proportion of the total allowable catch allocated to single-stock fisheries (*Section 2.2*). We also included a range of alternative operating models (*Section 2.3*) that incorporated adjustments to population productivity and the timing of en route mortality during freshwater migrations relative to fisheries.  

## 2.1 Reference operating model

We focused our analysis on the summer-run MU (one of four MUs in the Fraser River), which contains six stocks that vary in status. Summer-run sockeye salmon generally mature at age-4 (range in mean among summer-run stocks is `r round(min(cuPar$meanRec4), 2)`-`r round(max(cuPar$meanRec4), 2)`), with smaller proportions of age-3 and age-5 spawners. The stock-recruit time series cover `r diff` years, beginning in `r minY` and ending with the `r maxY` brood year. Note that throughout this manuscript we use *return* abundance to refer to the sum of catch and escapement in a given return year, where escapement is defined as the number of fish that have escaped all fisheries. In comparison, we use *recruit* abundance to refer to the sum of catch and escapement produced by spawners from a given brood year [@Grant2011].

We parameterized the operating models that were used to forward simulate stock dynamics in the analysis by fitting stock-recruit models (details below) to observed spawner and recruit abundance data. Pacific Salmon Commission and government agency stock assessment biologists perform run reconstructions annually under a bi-national Pacific Salmon Treaty process, in which observed escapement, catch, and age composition data are allocated to individual stocks based on microsatellite stock identification to generate estimates of abundance (reviewed in detail in Grant [-@Grant2011]). 

The structure of the operating model used to simulate population dynamics is equivalent to that in Freshwater et al. (2019). Briefly, we used an age-structured, Ricker model [@Ricker1975]

Equation 1  $$log_e(\frac{R_{i,y}}{S_{i,y}}) = \alpha_i - \beta_iS_{i,y} + w_{i,y}$$

where $i$ represents a stock, $y$ a given brood year, $R$ the number of recruits, and $S$ the number of spawners. $\alpha$ represents the number of recruits produced per spawner at low abundance (in log space), while $\beta$ is the density-dependent parameter (i.e. the reciprocal of spawner abundance maximizing recruitment). Recruitment deviations $w_{i,y}$ are normally distributed with mean 0 and variance $\sigma_{i}^2$.

Several Fraser River stocks are cyclic, exhibiting large differences in abundance at four-year intervals. To simulate the dynamics of cyclic stocks (two of six stocks in the Summer Run MU), we used a Larkin model, an extension of the Ricker model that accounts for delayed-density dependent effects [@Larkin1971]

Equation 2 $$log_{e}(\frac{R_{i,y}}{S_{i,y}}) = \alpha_i - \beta_{0,i}S_{i,y} - \beta_{1,i}S_{i,y-1} - \beta_{2,i}S_{i,y-2} - \beta_{3,i}S_{i,y-3} + w_{i,y}$$

where $\beta_{x}$ is the density-dependent parameter at time lag $x =$ 0, 1, 2, 3, 4. Fraser River sockeye salmon stocks modeled with a Larkin relationship contain one dominant and three off-cycle lines.

We initialized the simulation with stock-specific time series of spawner and recruit abundance and ran the simulation for `r simPar[["simYears"]][1]` years (approximately `r round(simPar[["simYears"]][1]/4, 0)` generations). To account for productivity declines in Fraser River sockeye salmon [@Peterman2012; @Freshwater2018], we used a recursive Bayes stock-recruitment model to estimate non-stationary $\alpha_i$ parameters from the historical time series. The priors for most parameters were weakly informative as in Pestal et al. [-@Pestal2011] (Table A1), except for $\alpha_i$ which was normally distributed with a mean, $\alpha_{stat,i}$ and standard deviation, $\sigma_{{alpha}_{stat},i}$, taken from the posterior estimates of a stationary stock recruit analysis [@Freshwater2019]. We fit models using MCMC in JAGS [@Plummer2003] with the R package R2jags [@Su2015]. We confirmed model convergence using visual inspection of trace plots and Gelman-Rubin statistics. Each model run included four MCMC chains of 32,500 iterations, with a burn in of 15,000 and a thinning rate of 7. We parameterized the forward simulation model with median parameter sets (i.e. median $\alpha_i$ from the most recent complete brood year and corresponding $\beta_i$ and $\sigma_i$) estimated from stock-specific models. 

The simulation model included multiple sources of mortality in addition to the natural mortality implicit in spawner-recruit relationships. First, we simulated harvest, $C$, in mixed- and single-stock fisheries (details in *Section 2.2*). Second, we simulated stock-specific en route mortality, $D$, which accounts for natural mortality during upstream migration, unreported harvest, post-release fishing mortality, and error between in-river and terminal estimates of spawner abundance [@Grant2011]. In the reference case en route mortality occurred after both mixed- and single-stock fisheries (but see *Section 2.3*). We modeled en route mortality as a stock-specific, stochastic process

Equation 3a $$ D_{i,t} = d_{i}(R'_{i,t} - C_{i,t})\epsilon_{mort,i,t} $$
Equation 3b $$ \epsilon_{mort,i,t} \sim \text{lognormal}(0, \sigma^2_{mort,i}) $$

where $R'_{i,t}$ is return abundance (all age classes) to stock $i$ in return year $t$, $d$ represents the mean (range among stocks 0.04-0.60), and $\sigma_{mort}$ the interannual standard deviation of estimated stock-specific en route mortality (range among stocks 0.17-0.48). $d$ and $\sigma_{mort}$ were parameterized using observed differences in abundance between in-river and spawning ground sampling sites (2000-2016; Pacific Salmon Commission, unpublished data). Like spawner abundance, catch, and age composition, en route mortality is estimated annually during the Fraser River sockeye salmon run reconstruction.

Spawner abundance $S$ was then calculated as 

Equation 4 $$ S_{i,t} = R'_{i,t} - C_{i,t} - D_{i,t}.$$

Additional operating model components, including temporal autocorrelation and among-stock covariance in simulated recruitment deviations, $w_{i,y}$, as well as interannual variation in age-at-maturity, are described in Appendix A.

## 2.2 Management procedure

The management procedure contained a harvest component, representing removals by mixed- and single-stock fisheries, as well as components that simulated data collection and assessed status relative to management targets. Briefly, we modeled tradeoffs between mixed- and single-stock fisheries by generating a target total allowable catch based on aggregate abundance relative to mixed-stock reference points (derived from aggregate stock-recruit dynamics). Next, a fixed proportion of the target catch (ranging from 0 to 1) was allocated to each stock's single-stock fishery, but was only harvested when a stock's status exceeded its unique reference points (details below). Thus target harvest rates differed among mixed- and single-stock fisheries because they responded to aggreagte and stock-specific reference points, respectively. Although the stock-selectivity of a fishery can be increased using various spatial or temporal restrictions, we modeled fully segregated and sequential fisheries. This structure maximized contrast between different allocations and is plausible for salmon where terminal fisheries have already been developed for several stocks [@DFO2017a].

We modeled catch in each fishery in three steps. First, an MU-level target exploitation rate, $u_{targ}$, was calculated based on aggregate abundance, using a generic harvest control rule proposed under Fisheries and Oceans Canada's Precautionary Approach Framework [@DFO2009]. Specifically, a minimal exploitation rate (0.005) was applied when MU-level abundance was less than 40% of the spawner abundance that would lead to maximumum sustainable yield ($0.4{S}_{MSY}$). When abundance was greater than 80% of that spawner abundance ($0.8{S}_{MSY}$), the exploitation rate at maximum sustainable yield (approximated by ${u}_{MSY}$) was applied (Fig. A1). When return abundance was between these two reference points, the target total exploitation rate was a linear function of abundance:

Equation 5 $$ u_{total} = {u}_{MSY}({\frac{R' – 0.4{S}_{MSY}} {0.8{S}_{MSY} − 0.4{S}_{MSY}}}).$$

We calculated ${u}_{MSY}$ at the aggregate MU-level using the Lambert W function, $W(z)$ [@Scheuerell2016]:

Equation 6 $$ {u}_{MSY} = 1 - W(e^{1 - \alpha_m})$$

where $\alpha_m$ is an estimate of MU-level productivity calculated by fitting a Ricker model (Eq. 2) to spawner and recruit abundance data summed among all summer-run stocks. Aggregate reference points were estimated from the sum of spawner and return abundances among stocks.

Second, we calculated stock-specific target catch for each fishery ($C_{targ,mix,i}$ and $C_{targ,sing,i}$) by applying target total exploitation rates to stock-specific return abundances as

Equation 7a $$ C_{targ,mix,i,t} = pu_{total}R'_{i,t} $$
Equation 7b $$ C_{targ,sing,i,t} = (1 - p)u_{total}R'_{i,t} $$

where $R'$ is return abundance and $p$ is the proportion of the total catch allocated to the mixed- versus single-stock fisheries. We varied $p$ from 0 to 1, in increments of 0.25, to evaluate the impact of changing the relative proportion of catch harvested in each fishery. Note that $C_{targ}$ calculations assume that _proportional_ stock-specific return abundance is known without error, which may result in overestimates of single-stock fishery performance (see Appendix A for details including justification).

Third, we reduced fishery impacts on depleted stocks by closing single-stock fisheries when median observed stock-specific spawner abundance during the previous generation, $\tilde{S}_{med, i}$, was below a threshold consistent with conservation concern, $S_{con, i}$. In the case of non-cyclic stocks (Ricker model) the single-stock harvest control rule was

Equation 8a $$ C_{targ,sing,i,t} = 0 \text{ if  } \tilde{S}_{med,i} < S_{con,i}, $$

where

Equation 8b $$ \tilde{S}_{i,t} = S_{i,t}\epsilon_{obs,i,t} $$ 
Equation 8c $$ \epsilon_{obs,i,t} \sim \text{lognormal}(0, \sigma^2_{obs,i}) $$

with observed spawner abundance, $\tilde{S}_{i,t}$, differing from true spawner abundance to simulate run-reconstruction estimation processes.

In the case of cyclic stocks (Larkin model) the single-stock fishery was closed ($C_{targ,sing,i,t} = 0$) unless the current simulation year was a dominant cycle line (defined by calendar year) and the previous dominant return year's spawner abundance was greater than ${S}_{con,i}$ [@DFO2018a]. We defined $S_{con,i}$ as the abundance that will result in spawner abundance leading to ${S}_{MSY,i}$ in one generation in the absence of fishing mortality (i.e. ${S}_{gen,i}$ [@Holt2009]). 

We included outcome uncertainty so that realized catches deviated from target catches, representing the cumulative effects of forecast error, misreported catch, and lack of enforcement [@Holt2006]. We simulated realized exploitation rates $u$ for each fishery $f$ (where $f$ corresponds to either $mix$ or $sing$) using a beta distribution:

Equation 9a $$ u_{f,i,t} \sim \text{beta}(a_{f,i,t}, b_{f,i,t})$$

where $a$ and $b$ were calculated from target fishery-specific exploitation rates $u_{targ,f}$ and empirical estimates of deviations between target and realized exploitation rates, $\sigma_{out}$, as follows:

Equation 9b $$ a_{f,i,t} = u_{targ,f,i,t}^2 ({\frac{1 - u_{targ,f,i,t}} {\sigma_{out}^2}} - {\frac{1}{u_{targ,f,i,t}}}) $$
Equation 9c $$ b_{f,i,t} = a_{f,i,t}({\frac{1} {u_{targ,f,i,t}}} - 1) $$
Equation 9d $$ u_{targ,f,i,t} = {\frac{C_{targ,f,i,t}} {R'_{i,t}}}. $$

We estimated $\sigma_{out}$ as the difference between target and realized exploitation rates in mixed-stock fisheries for Fraser River sockeye salmon MUs between 2006 and 2017. We fixed $\sigma_{out}$ at $`r simPar[["mixOUSig"]][1]`$ for both mixed- and single-stock fisheries since marine and in-river fisheries have similar deviations from management targets (J. Scroggie, DFO Fisheries Management, *personal communication*). 

Finally we calculated realized catches for each fishery ($C_{mix,i}$ and $C_{sing,i}$) by applying realized exploitation rates to stock-specific return abundances as

Equation 10a $$ C_{mix,i,t} = u_{mix,i,t}R'_{i,t} $$
Equation 10b $$ C_{sing,i,t} = u_{sing,i,t}(R'_{i,t} - C_{mix,i,t}). $$

Note that Fraser River sockeye salmon are managed with a more conservative harvest control rule (total allowable mortality (TAM) rule), that accounts for cyclic abundance, overlapping run timings among MUs, en route mortality, and other system-specific management adjustments [@Pestal2011]. However the reference points associated with the TAM rule vary interannually and are informed by expert opinion, reducing its relevance to salmon fisheries in general. The TAM rule is summarized in Appendix A and we present the results of a secondary analysis comparing its performance to the generic harvest control rule.

## 2.3 Alternative operating models

We evaluated the performance of different fishery allocations across alternative operating models to explore how trade-offs in conservation- and catch-based objectives might be affected. First, we incorporated different levels of productivity by applying a scalar (0.6 to 1.1 in increments of 0.05) to $\alpha_{i}$. The scalar's bounds were based on observed productivity changes (mean ~30% decline, ranging from 54% decline to 53% increase) and represented hypothetical future changes that might mirror those that have already occurred. 

Second, we modeled the impact of single-stock harvest that occurred after en route mortality

Equation 11 $$ C_{sing,i,t} = u_{sing,i,t}(R'_{i,t} - C_{mix,i,t} - D_{i,t}). $$

Thus spawner abundance was calculated as

Equation 12 $$ S_{i,t} = R'_{i,t} - C_{mix,i,t} - D_{i,t} - C_{sing,i,t}, $$

which represents a scenario where single-stock fisheries are fully terminal. 

Additionally, we completed sensitivity analyses to evaluate the impact of our assumptions about the magnitude of: temporal autocorrelation in recruitment deviations ($\tau$), error associated with estimating spawner abundance ($\sigma_{obs}$), outcome uncertainty ($\sigma_{out}$), and interannual variability in age-at-maturity ($\gamma$) and en route mortality ($\sigma_{mort}$) (Appendix B).

## 2.4 Performance metrics

We considered multiple conservation- and catch-based performance metrics to determine how fishery allocations impact management performance (Table \@ref(tab:pmTable)). We evaluated both aggregate (i.e. summed or mean values within the MU) and stock-specific performance metrics. Note that we use reference points to denote levels of abundance that trigger a change in harvest rates and biological benchmarks to represent abundance thresholds associated with conservation status. We present median outputs, as well as the 5th and 95th percentiles, among simulations for each performance metric. We summarized performance metrics across 1500 Monte Carlo trials (convergence occurred after approximately 1200). The simulation model is available in the _samSim_ package (available at https://github.com/CamFreshwater/samSim) and the code necessary to run the analyses are available at https://doi.org/10.5281/zenodo.3432483.

```{r pmTable, results="asis"}
pmTable <- read.csv(here::here("data", "msTables", "pmTable.csv"))

k <- knitr::kable(pmTable, format = "pandoc", booktabs = TRUE, linesep = "",
                  caption = "Aggregate and stock-specific performance metrics.",
                  "latex") 
k <- kableExtra::kable_styling(k, font_size = 12)
k
```