# 3. Results 

```{r loadSimRunData, include=FALSE}
library(samSim)
library(ggpubr)
library(tidyverse)
## Simulation ran in varyAllocation_mainSimRun.R, which also includes example figures
simPar <- read.csv(here::here("data", "manProcScenarios",
                        "fraserMPInputs_varyAllocationVaryMixHCR.csv"),
                   stringsAsFactors = F)
simParTrim <- simPar %>%
  filter(nameOM %in% c("ref", "enRoute"),
         benchmark == "stockRecruit")
scenNames <- unique(simParTrim$scenario)
dirNames <- sapply(scenNames, function(x) paste(x, unique(simParTrim$species), 
                                                sep = "_"))

#ID stocks included in CU-specific analyses
# cuPar <- read.csv(here::here("data", "old", "fraserCUPars.csv"),
#                   stringsAsFactors = F)
cuPar <- read.csv(here::here("data/summOnlyCUPars.csv"), stringsAsFactors = F)
summCUs <- cuPar %>% 
  mutate(abbStkName = abbreviate(stkName, minlength = 4)) %>% 
  select(abbStkName) %>% 
  unlist()

agVarsToPlot <-  c("medRecRY", "medSpawners", "ppnCULower", 
                   "medCatch", "stabilityCatch", "medER")

agDat <- buildDataAgg(dirNames, agVars =  agVarsToPlot, 
                      keyVarName = "ppnMixed") %>%
  mutate(mp = case_when(
    str_detect(mp, "genPA") ~ "Generic",
    str_detect(mp, "TAM") ~ "TAM"
  ), 
  labelledVar = var) %>%
  mutate(mp = as.factor(mp), 
         labelledVar = fct_recode(labelledVar, 
                                  "Aggregate\nReturn Abundance" = "medRecRY",
                                  "Aggregate\nSpawner Abundance" = 
                                    "medSpawners",
                                  "Proportion of CUs\nAbove Cons. BM" = 
                                    "ppnCULower",
                                  "Aggregate\nCatch" = "medCatch",
                                  "Catch\nStability" = "stabilityCatch",
                                  "Median\nExploitation Rate" = "medER")) 

refDat <- agDat %>% 
  filter(om == "ref", 
         mp == "Generic") 
```

Aggregate conservation performance declined as the proportion of total allowable catch allocated to mixed-stock fisheries increased. Median (among simulation years) return abundance, median spawner abundance, and the mean proportion of stocks above their conservation benchmark decreased as mixed-stock allocations grew (Fig. 1a-c). Conversely median aggregate catch and catch stability were maximized at intermediate allocations to mixed-stock fisheries (Fig. 1d,e). Impacts on conservation- and catch-based metrics were driven by differences in realized exploitation rates (Fig. 1f), which increased with mixed-stock fishery allocations.

```{r Fig1, warnings=FALSE, messages=FALSE, fig.cap="Changes in aggregate conservation- and catch-based performance metrics across a range of fishery allocations, i.e. range of proportional allocation of mixed- to single-stock where 1 and 0 are fully mixed- and fully single-stock fisheries, respectively. Circles represent medians and whiskers represent 90th percentile intervals among Monte Carlo trials. Abundance and catch are in millions of fish."}
colPal <- viridis::viridis(length(levels(refDat$ppnMixed)), begin = 0,
                           end = 1, option = "plasma")
# colPal <- grDevices::gray.colors(n = length(levels(refDat$ppnMixed)), 
#                                  start = 0.9, end = 0.1)
names(colPal) <- levels(refDat$ppnMixed)

panelLabs <- data.frame(lab = c("a)", "b)", "c)", "d)", "e)", "f)"),
                        var = factor(agVarsToPlot, 
                                     levels = unique(agVarsToPlot)))

agDotPlotList <- lapply(seq_along(agVarsToPlot), function(x) {
  dum <- refDat %>% 
    filter(var == agVarsToPlot[x])
  p <- ggplot(dum, aes(x = ppnMixed, y = avg, ymin = lowQ, ymax = highQ)) +
    ylim(0.85 * min(dum$lowQ), max(dum$highQ)) +
    labs(x = "", y = unique(dum$labelledVar)) +
    geom_pointrange(shape = 21, fatten = 2.5, size = 2,
                    position = position_dodge(width = 0.65), 
              fill = "white") +
    geom_text(data = panelLabs %>% filter(var == agVarsToPlot[x]),
              mapping = aes(x = 0.9, y = min(0.85 * dum$lowQ), label = lab,
                            vjust = 0),
              show.legend = FALSE, inherit.aes = FALSE, size = 5) 
  # +
  #   scale_fill_manual(guide = FALSE, values = colPal)
  if (unique(dum$var) %in% c("medRecRY", "medSpawners", "ppnCULower")) {
    p <- p +
      theme_sleekX(position = "top", axisSize = 15)
  } else {
    p <- p +
      theme_sleekX(position = "bottom", axisSize = 15)
  }
  return(p)
})

panelFig <- ggarrange(agDotPlotList[[1]], agDotPlotList[[2]], 
                      agDotPlotList[[3]], agDotPlotList[[4]],
                      agDotPlotList[[5]], agDotPlotList[[6]],
                  ncol = 3, nrow = 2, align = "v", heights = c(0.85, 1.1))
annotate_figure(panelFig, bottom = text_grob("Proportion Mixed-Stock TAC",
                                             size = 17, vjust = -1))
```

```{r recDecline, include=FALSE}
f <- function(ppnM, V = "medRecRY") {
  refDat %>% 
    filter(var == V, ppnMixed == ppnM) %>% 
    select(avg) %>% 
    as.numeric()
}
recDecline <- round((f(ppnM = "0") - f(ppnM = "0.5")) / f(ppnM = "0"), 
                    digits = 2) * 100
ppnDecline <- round((f(ppnM = "0", V = "ppnCULower") - f(ppnM = "0.5", 
                                                         V = "ppnCULower")) / 
                      f(ppnM = "0", V = "ppnCULower"), 
                    digits = 2) * 100
```

Mixed- and single-stock fishery allocations consistently lead to different trade-offs between aggregate conservation- and catch-based objectives. Fully single-stock fisheries resulted in the greatest conservation performance, but considerably lower median catches, while fully mixed-stock fisheries maximized neither conservation nor catch performance. Conversely, intermediate allocations, for example splitting total allowable catch evenly between mixed- and single-stock fisheries, led to high median catches and relatively high median return abundance (`r recDecline`% decline relative to fully single-stock fisheries; Fig. \@ref(fig:Fig2)a) and a high mean proportion of stocks above their conservation benchmark (`r ppnDecline`% decline; Fig. \@ref(fig:Fig2)b). 

```{r Fig2, warnings=FALSE, messages=FALSE, fig.cap="Trade-offs between aggregate conservation- and catch-based performance metrics across a range of mixed-stock fishery allocations. Points represent medians and whiskers represent 90th percentile intervals among Monte Carlo trials."}
# Fig. 2 - Agg tradeoff plots
consVec <- c("medRecRY", "ppnCULower")
catchVec <- rep(c("medCatch"), times = length(consVec))
conLabels <- c("Median Aggregate\nReturn Abundance", 
               "Proportion of Stocks\nAbove Benchmark")
panelLabs <- data.frame(lab = c("(a)", "(b)"),
                        var = factor(consVec, 
                                     levels = unique(consVec)))
dum <- refDat %>% 
  filter(var == "medCatch")

toAgList <- lapply(seq_along(consVec), function(x) {
  p <- plotAgTradeoff(refDat %>% select(-labelledVar), consVar = consVec[x], 
                      catchVar = catchVec[x],
                      facet = NULL, shape = NULL, showUncertainty = TRUE,
                      xLab = "", yLab = conLabels[x], 
                      legendLab = "Proportion\nMixed-Stock\nTAC",
                      axisSize = 14, dotSize = 6, legendSize = 14,
                      lineSize = 1.5, scaleAxis = "fixed", hotColors = TRUE) +
    geom_text(data = panelLabs %>% filter(var == consVec[x]),
              mapping = aes(x = max(0.97 * dum$highQ), y = Inf, label = lab,
                            vjust = 1.5),
              show.legend = FALSE, inherit.aes = FALSE, size = 6)
  return(p)
})
panelTO <- ggarrange(toAgList[[1]], toAgList[[2]], ncol = 2, nrow = 1,
                             common.legend = TRUE, legend = "right")
annotate_figure(panelTO, bottom = ggpubr::text_grob("Median Aggregate Catch",
                                                   size = 15, vjust = -0.5))
```

Trade-offs were more nuanced at the scale of individual stocks. For example, abundant and relatively productive stocks either were insensitive (Harrison, Fig. \@ref(fig:Fig3)) or responded positively (Chilko, Fig. \@ref(fig:Fig3)) to increases in mixed-stock fishery allocations. In both cases, single-stock fisheries were rarely closed because the stock typically remained above its biological benchmark, resulting in exploitation rates that were similar among fishery allocation frameworks. In the case of the Chilko stock, rare single-stock closures had negative impacts because they resulted in large spawner abundances that exceeded capacity and reduced abundance in subsequent years. More commonly, however, larger mixed-stock fishery allocations resulted in  declines in return abundance and ultimately catch due to recruitment overfishing (Fig. \@ref(fig:Fig3)). These effects were particularly severe in the least abundant stock, Raft, which exhibited strong declines in abundance when mixed-stock fishery allocations exceeded 25% of total allowable catch (Fig. \@ref(fig:Fig3)). For other stocks abundance declined when mixed-stock allocations exceeded 50%.

```{r Fig3, warnings=FALSE, messages=FALSE, fig.cap="Trade-offs between stock-specific return abundance and catch across a range of mixed-stock fishery allocations. Points represent medians and whiskers represent 90th percentile intervals among Monte Carlo trials."}
cuVarsToPlot <- c("medRecRY", "medSpawners", "medCatch", "ppnYrsUpper",
                  "medTotalER")

cuDat <- buildDataCU(dirNames = dirNames, 
                     cuVars = cuVarsToPlot,
                     keyVarName = "ppnMixed", 
                     selectedCUs = summCUs) %>% 
  mutate(ppnMixed = as.factor(ppnMixed),
         mp = case_when(
           str_detect(mp, "genPA") ~ "Generic",
           str_detect(mp, "TAM") ~ "TAM"
         ),
         cuName = fct_recode(cuName, "L. Stuart" = "L.St", "Stellako" = "Stll",
                        "Quesnel" = "Qsnl", "Chilko" = "Chlk", "Harrison" = 
                          "Hrrs")) %>% 
  select(-plotOrder, -muName) %>% 
  filter(om == "ref",
         mp == "Generic")

p <- plotCUTradeoff(cuDat, consVar = "medRecRY", catchVar = "medCatch",
               facet = "cu", panel = "om", showUncertainty = TRUE,
               xLab = "Median Catch", yLab = "Median Return Abundance",
               legendLab = "Proportion\nMixed-Stock\nTAC", lineSize = 0.75, 
               main = FALSE, axisSize = 15, dotSize = 4, hotColors = TRUE)
p[[1]]
```

```{r heatMapdata, include=FALSE}
heatMapDat <- readRDS(here::here("outputs", "generatedData", "heatMapDat.rds"))
prodDat <- heatMapDat %>% 
  dplyr::filter(scenario == "Prod")

plotHeat <- function(plotVar = "medRecRY", legName = "rec", bins = 30,
                     dat = agDat) {
  dum <- dat %>%
    filter(var == plotVar) %>% 
    mutate(xAxis = case_when(
      scenario == "Synch" ~ synch,
      scenario == "Prod" ~ prod
    ))
  dumInterp <- akima::interp(x = dum$xAxis, y = dum$ppnMixedNew, 
                             z = dum$avg, nx = bins, ny = bins) %>% 
    akima::interp2xyz() %>% 
    as.data.frame()
  names(dumInterp) <- c("opMod", "ppnMixedNew", "value")
  ggplot(dumInterp, aes(x = opMod, y = ppnMixedNew)) + 
    geom_tile(aes(fill = value)) + 
    geom_contour(aes(z = value), color = "black", linetype = 1, size = 1.1) +
    # scale_fill_gradient(name = legName, low = "#0D0D0D", high = "#E6E6E6") +
    viridis::scale_fill_viridis(name = legName, option = "plasma") +
    theme_sleekX(legendSize = 1.1, axisSize = 14) +
    theme(axis.title.x = element_blank(),
          axis.title.y = element_blank())
}
```

Changes in population productivity altered the effect of fishery allocations on conservation- and catch-based metrics. At high levels of productivity, increasing single-stock fishery allocations resulted in relatively large increases in the proportion of stocks above the conservation threshold; however as productivity declined the relative difference between predominantly mixed- and single-stock fisheries decreased (Fig. \@ref(fig:Fig4) left). Conversely, median catch was maximized at intermediate allocations (~75% mixed stock) when productivity was high, but as productivity declined predominantly single-stock fisheries began to provide slightly greater catches (Fig. \@ref(fig:Fig4) right). 

```{r Fig4, warnings=FALSE, messages=FALSE, fig.cap="Impacts of changes in productivity on median proportion of stocks above their conservation benchmark, $S_{con}$ (left) and median aggregate catch (right) across a range of mixed-stock fishery allocations. Productivity is moderated by a scalar applied uniformly to the most recent estimate for each stock so that the data shown with productivity scalar = 1 is equivalent to Fig. 2b."}
dumLab <- expression(atop('Ppn. Stocks', 'Above S'[con]))
ppnProd <- plotHeat(plotVar = "ppnCULower", 
                    legName = dumLab,
                    dat = prodDat)
catchProd <- plotHeat(plotVar = "medCatch", legName = "Catch",
                    dat = prodDat)

panelHeat <- ggarrange(ppnProd, catchProd,  ncol = 2, nrow = 1, 
                       widths = c(1.15, 1))
annotate_figure(panelHeat, bottom = text_grob("Productivity Scalar", size = 15,
                                              vjust = -0.5),
                left = text_grob("Proportion Mixed-Stock TAC", size = 15, 
                                 rot = 90))
```

Trade-offs between mixed- and single-stock fisheries were also sensitive to the structure of the harvest control rule. A more precautionary mixed-stock harvest control rule, which mimicked the framework currently used by Fraser River sockeye salmon managers, still resulted in relatively larger catches in mixed-stock fisheries, but did not exhibit evidence of recruitment overfishing (i.e. no backward bending curve as the poroportion of mixed-stock fisheries increased) (Fig. \@ref(fig:Fig5)a,b). Additionally, declines in conservation-based performance metrics with predominantly mixed-stock fisheries were more modest than those observed with the reference, generic mixed-stock harvest control rule (Fig. \@ref(fig:Fig5)a,b).

```{r Fig5, warnings=FALSE, messages=FALSE, fig.cap="The impact of an alternative mixed stock harvest control rule (b) and en route mortality prior to single-stock fisheries (c), on trade-offs between aggregate return abundance and catch. Points represent medians and whiskers represent 90th percentile intervals among Monte Carlo trials. Note that panel (a) is the same as Fig. 2a and is presented here to facilitate comparison."}
altOMDat <- agDat %>% 
  mutate(om = case_when(
    str_detect(om, "enRoute") ~ "En Route Mortality\nBefore Fishery",
    str_detect(om, "ref") & hcr == "genPA" ~ "Reference",
    hcr == "TAM" ~ "TAM Rule"
  ),
  hcr = case_when(
    hcr == "genPA" ~ "Generic",
    TRUE ~ "TAM"
  )) %>% 
  mutate(om = fct_relevel(om, "Reference", "TAM Rule"))
omVec <- unique(altOMDat$om)
panelLabs <- data.frame(lab = c("(a)", "(b)", "(c)"),
                        om = factor(omVec, levels = omVec))
labY <- altOMDat %>% 
  filter(var == "medRecRY") %>% 
  select(lowQ) %>% 
  min()
labX <- altOMDat %>% 
  filter(var == "medCatch") %>% 
  select(lowQ) %>% 
  min()

plotAgTradeoff(altOMDat %>% select(-labelledVar), consVar = "medRecRY", 
               catchVar = "medCatch", facet = "om", 
               shape = NULL, showUncertainty = TRUE, 
               xLab = "Median Aggregate Catch", 
               yLab = "Median Aggregate Return", 
               legendLab = "Proportion\nMixed-Stock\nTAC",
               axisSize = 13, dotSize = 5, legendSize = 12, lineSize = 1,
               scaleAxis = "fixed", hotColors = TRUE, facetLetter = TRUE)


med_decline <- altOMDat %>% 
  filter(var %in% c("medRecRY", "medCatch"),
         !om == "TAM Rule",
         ppnMixed %in% c(0.5, 0)) %>% 
  group_by(ppnMixed, var) %>% 
  summarize(prop_dec = round(1 - (min(avg) / max(avg)), digits = 2),
            perc_dec = paste(prop_dec * 100, "%", sep = ""))
sing_rec <- med_decline %>% 
  filter(ppnMixed == "0", 
         var == "medRecRY")
sing_catch <- med_decline %>% 
  filter(ppnMixed == "0", 
         var == "medCatch")

```

The final model adjustment we considered was shifting the timing of en route mortality to precede single-stock fishery harvest, representing a fully terminal harvest scenario. This change resulted in reduced performance of single-stock fisheries. For example, median aggregate return abundance in the fully single-stock management procedure declined by `r sing_rec$perc_dec` relative to the reference operating model and median aggregate catch declined by `r sing_catch$perc_dec` (Fig. \@ref(fig:Fig5)a,c). Conversely, this adjustment had only modest impacts on management procedures with intermediate fishery allocations or fully mixed-stock fisheries.
