---
header-includes:
  - \usepackage{caption}
output:
  word_document:
    fig_caption: yes
    #reference_docx: templates/blankMS.docx
  # bookdown::pdf_document2:
  #   fig_caption: yes
  #   latex_engine: pdflatex
    # includes:
    #   in_header: preamble-latex.tex
csl: csl/ecology.csl
link-citations: no
bibliography: bib/ms_singleStock.bib
---

```{r setup, echo=FALSE, cache=FALSE, message=FALSE, results='hide', warning=FALSE}
# adjust as desired:
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.path = if (knitr:::is_latex_output()) "knitr-figs-pdf/" else "knitr-figs-docx/",
  cache.path = if (knitr:::is_latex_output()) "knitr-cache-tex/" else "knitr-cache-docx/",
  fig.asp = 0.618,
  fig.width = 9,
  out.width = "6in",
  echo = FALSE,
#  autodep = TRUE,
#  cache = TRUE,
  cache.comments = FALSE,
  dev = if (knitr:::is_latex_output()) "png" else "png",
  dpi = 180,
  fig.align = "center",
  fig.pos = "htb"
)
options(kableExtra.latex.load_packages = FALSE)
```

```{r load-libraries, cache=FALSE}
# add other packages here:
library(csasdown)
library(here)
library(tidyverse)
library(samSim)
library(knitr)
library(kableExtra)

simPar <- read.csv(here::here("data", "manProcScenarios",
                        "fraserMPInputs_varyAllocationVaryMixHCR.csv"),
                   stringsAsFactors = F)
cuPar <- read.csv(here::here("data/summOnlyCUPars.csv"), stringsAsFactors = F)
```

# Appendix A - Supplementary Methods

## 1. Operating Model

```{r priorsTable, results="asis"}
priorsTable <- read.csv(here::here("data", "msTables", "priorsTable.csv"))
#add parameters 
parPriors <- c("ln$(\\alpha)$", "$S_{max}$", "$\\tau$", "$\\beta_{1-3}$")
dist <- c("normal$(\\alpha_{stat}, \\sigma^2_{\\alpha_{stat}})$",
          "lognormal(ln(max$(S_{obs.}), 1)$ truncated at 3 x max$(S_{obs.})$",
          "gamma(0.001, 0.001)",
          "uniform(0, 100")
priorsTable <- priorsTable %>% 
  mutate(Parameter = parPriors, 
         Prior.Distribution = dist)
csas_table(priorsTable,
  caption = "Table A1. Priors for recursive Bayes stock recruit models.",
  font_size = 20,
  col_names = c("Parameter", "Description", "Prior Distribution")
)
```

### 1.1 Recruitment deviations

Year- and stock-specific recruitment deviations $w_{i,y}$ in the forward simulation incorporated temporal autocorrelation and covariance in recruitment deviations among stocks

Equation A1a $$w_{i,y} = w_{i,y-1}\tau + r_{i,y}$$
Equation A1b $$r_i \sim MVN(0, \boldsymbol{\mathrm{V}})$$
Equation A1c $$\boldsymbol{\mathrm{V}} =
 \begin{bmatrix}
  \sigma'^2_1 & \rho\sigma'_1\sigma'_2 & \cdots & \rho\sigma'_1\sigma'_n \\
  \rho\sigma'_1\sigma'_2 & \sigma'^2_2 & \cdots & \rho\sigma'_2\sigma'_n \\
  \vdots  & \vdots  & \ddots & \vdots  \\
  \rho\sigma'_1\sigma'_n & \rho\sigma'_2\sigma_n & \cdots & \sigma'^2_n
 \end{bmatrix}$$
 
where $w_{i,y-1}$ represents recruitment deviations one year prior, $\tau$ represents an autoregressive lag-1 year (AR1) correlation coefficient, and $r_{i,y}$ represents multivariate normally distributed error with a standard deviation defined by the variance-covariance matrix $\boldsymbol{\mathrm{V}}$, dimensioned by the number of stocks $n$. $\rho$ represents the pairwise correlation coefficient among stocks and was set to $`r simPar[["correlCU"]][1]`$ based on the mean observed correlation in recruitment deviations in recent years. We adjusted estimates of $\sigma$ downwards from values in Eq. 1 to account for additional autocorrelated variability, $\tau$, using the transformation, $\sigma'^2 = \sigma^2(1-\tau^2 )$, where $\sigma^2$ is the variance derived from a model without autocorrelation and $\sigma'^2$ is the adjusted value [@Pestal2011]. $\tau$ was set to 0.2 based on evidence of weak autocorrelation in the residuals of stock-recruit models from preliminary analyses.

### 1.2 Age-at-maturity

Although the majority of Fraser River sockeye salmon mature at age 4 (i.e. one winter as eggs, one winter as fry in lakes, and two ocean winters), smaller proportions mature at ages 2, 3, and 5, with age structure varying among stocks. We modeled this process by calculating the number of individuals returning to spawn $R'_{i,t}$ in return year $t$ in stock as a function of the total number of adult recruits $R$ generated in previous brood years, multiplied by the proportion $p$ of fish that return at a given age $g$ 

Equation A2 $$ R'_{i,t} = R_{i,t-2}p_{2,i,t-2} + R_{i,t-3}p_{3,i,t-3} + R_{i,t-4}p_{4,i,t-4} + R_{i,t-5}p_{5,i,t-5}. $$

We incorporated multivariate logistic variation in the proportion of mature fish returning at each age

Equation A3 $$ p_{g,i,y} = \frac{ \overline{p}_{g,y} e^{\gamma_i \omega_{g,i,y}}} {\sum_{2}^{5} \overline{p}_{g,y} e^{\gamma_i \omega_{g,i,y}}} $$

```{r gammas, include=FALSE}
minGamma <- min(cuPar$tauCycAge)
maxGamma <- max(cuPar$tauCycAge)
```

where $y$ is the brood year (equal to $t-2$, $t-3$, $t-4$ or $t-5$ in Eqn. 4), the summation in the denominator is over ages g= 2 to 5, $\overline{p}_{g,y}$ is the stock-specific mean proportion of adult fish that return at a given age, $\gamma$ is a parameter controlling interannual variability in the proportion returning at each age, and $\omega_{g,i,y} \sim \text{normal}(0, 1)$ [@Schnute1995; @Holt2011]. We estimated stock-specific $\gamma_i$ parameters, which scaled the size of deviations in Eq. A3, using a simple grid search of Fraser River sockeye salmon ages at maturity. Estimates of $\gamma_i$ ranged from $`r minGamma`$ - $`r maxGamma`$ among stocks.

## 2. Management procedure

### 2.1 Forecast error

The simulation model assumes that total catch is split into stock-specific target catch, $C_{targ,i}$, proportional to each stock's abundance in a given year. Although forecast errors in estimates of return abundance are not explicitly simulated here, data used to parameterize outcome uncertainty incorporated forecast error, as well as other sources of implementation error (e.g., misreported catch, delays in management action, lack of enforcement). We did not simulate the forecast process independently because there are no data available to parameterize forecast error independently of these other dimensions of implementation error, which would result in deviations between target and realized catch that are artificially inflated. Nevertheless, preliminary investigations suggest that incorporating forecast error when allocating aggregate total allowable catch to stock-specific catch may result in reduced performance of single-stock fisheries, relative to mixed-stock, due to intermittent overharvest of less abundant stocks (not shown).

### 2.2 Harvest control rules

```{r genHCR, warnings=FALSE, messages=FALSE, fig.cap="Figure A1. Generic, abundance-based harvest control rule used to calculate target exploitation rates. Dashed vertical lines represent lower (red) and upper (green) fishery reference points equivalent to $0.4{S}_{MSY}$ and $0.8{S}_{MSY}$, respectively. The maximum exploitation rate is equal to ${u}_{MSY}$ (0.66 for the Summer Run MU aggregate)."}
cuPar <- read.csv(here::here("data/summOnlyCUPars.csv"), stringsAsFactors = F)
uMsy <- cuPar$uMSY[1]
lowFRP <- cuPar$lowFRP[1]
highFRP <- cuPar$highFRP[1]
ret = seq(0, 2, length.out = 999)
esc = rep(NA, length.out = 999)
hr = rep(NA, length.out = 999)
for (i in 1:length(ret)) {
  if (ret[i] < lowFRP) {
    hr[i] <- 0.005
  }
  if (ret[i] > lowFRP & ret[i] < highFRP) {
    hr[i] <- max(0.005, 
                 uMsy * ((ret[i] - lowFRP) / (highFRP - lowFRP))
                 )
  }
  if (ret[i] > highFRP) {
    hr[i] <- uMsy
  }
  esc[i] <- ret[i] - (ret[i] * hr[i])
}
plot(hr ~ ret, xlim=c(0, 2), ylim=c(0, 1), ylab = "", xlab = "", axes = F, 
     type ="l", lwd = 2)
axis(1, las = 1)
axis(2, las = 1)
mtext("Total Exploitation Rate", 2, line = 2.5)
mtext("Return Abundance (Millions)", 1, line = 2)
abline(v = lowFRP, col = "red", lty = 2, lwd = 2)
abline(v = highFRP, col = "darkgreen", lty = 2, lwd = 2)
```

We evaluated the impact of an alternative HCR, a total allowable mortality (TAM) rule, intended to approximate the management framework currently used for Fraser River sockeye salmon. As with the generic, reference HCR, the TAM rule specifies annual target harvest rates based on return abundance relative to two fishery reference points. Unlike the generic HCR, however, the TAM rule reference points differ among cycle lines and were derived using expert knowledge [@Pestal2011]. In addition, the maximum target exploitation rates are lower than the $u_{MSY}$ value of 0.66 used in the generic HCR (Table A2).

```{r frpTable, results="asis"}
frpTable <- read.csv(here::here("data", "msTables", "frpTable.csv"))
csas_table(frpTable,
  caption = "Table A2. Fishery reference points (FRP; in millions of fish) and maximum exploitation rates (ER) for the generic harvest control rule utilized in the main text and the total allowable mortality rule. Note that the first year of the simulation is on the 4th cycle line.",
  font_size = 20,
  col_names = c("Harvest Control Rule", "Cycle", "Low FRP", "High FRP", "Maximum Target ER")
)
```

The TAM rule also differs from the generic HCR due to three additional adjustments. First, the TAM rule includes a constant escapement goal above the lower fishery reference point, resulting in a curvilinear increase in target exploitation rates as abundance increases, rather than the linear increase in Fig. A1. Second, harvest rates are often reduced by managers due to anticipated en-route mortality. We simulated this process by applying an en-route mortality adjustment, _pMA_, that acts as a scalar on escapement goals (the difference between return size and target catch). Thus a _pMA_ equal to 0 results in no adjustment, while a _pMA_ equal to 1 results in a 100% increase in the escapement goal. We parameterized this model component by setting the _pMA_ equal to the median _pMA_ observed for the Summer Run MU since 2000. Third, harvest rates are adjusted annually to reduce incidental harvest of co-migrating MUs that are at low abundance. We excluded this adjustment because we only modeled one MU (Summer Run stocks) here.

_Literature Cited_