---
header-includes:
  - \usepackage{caption}
output:
  word_document:
    fig_caption: yes
    reference_docx: templates/blankMS.docx
  # bookdown::pdf_document2:
  #   fig_caption: yes
  #   latex_engine: pdflatex
    # includes:
    #   in_header: preamble-latex.tex
csl: csl/ecology.csl
link-citations: no
bibliography: bib/ms_singleStock.bib
---

```{r setup, echo=FALSE, cache=FALSE, message=FALSE, results='hide', warning=FALSE}
# adjust as desired:
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.path = if (knitr:::is_latex_output()) "knitr-figs-pdf/" else "knitr-figs-docx/",
  cache.path = if (knitr:::is_latex_output()) "knitr-cache-tex/" else "knitr-cache-docx/",
  fig.asp = 0.618,
  fig.width = 9,
  out.width = "6in",
  echo = FALSE,
#  autodep = TRUE,
#  cache = TRUE,
  cache.comments = FALSE,
  dev = if (knitr:::is_latex_output()) "png" else "png",
  dpi = 180,
  fig.align = "center",
  fig.pos = "htb"
)
options(kableExtra.latex.load_packages = FALSE)
```


```{r loadData, include=FALSE}
library(csasdown)
library(here)
library(tidyverse)
library(samSim)
library(knitr)
library(kableExtra)

simPar <- read.csv(here::here("data", "manProcScenarios",
                        "fraserMPInputs_varyAllocationSens.csv"), 
                   stringsAsFactors = F) %>% 
  mutate(nameMP = paste(propMixHigh, singleHCR, "_", harvContRule, sep = ""))
cuPar <- read.csv(here::here("data/summOnlyCUPars.csv"), stringsAsFactors = F)

# Focal CUs and CU-specific PMs
summCUs <- cuPar %>% 
  filter(manUnit == "Summ") %>% 
  mutate(abbStkName = abbreviate(stkName, minlength = 4)) %>% 
  select(abbStkName) %>% 
  unlist()

# Summary sim data
plotDat <- read.csv(here::here("outputs", "generatedData", 
                               "sensAnalysisSummaryData.rds")) %>% 
  filter(mp == "0.5retro_genPA") %>% 
  mutate(scen = fct_relevel(scen, "rho", "obsSig", "mixOU", "singOU", "ageTau",
                            "enRouteSig"),
         om = fct_relevel(om, "low", "high"))
```


# Sensitivity analyses 

We conducted sensitivity analyses to evaluate how our conclusions may be impacted by the magnitude of temporal autocorrelation, observation error, outcome uncertainty, and interannual variation in stochastic parameters (age-at-maturity and en route mortality). For each parameter we selected upper and lower values (bounding plausible ranges; next paragraph and Table S3.1), held the remaining parameters constant, and compared performance metric distributions generated from 1500 Monte Carlo trials. We present results from a management procedure specifying equal allocations between mixed- and single-stock fisheries for all sensitivity scenarios. Additional analyses indicated that increasing the mixed-stock allocation increased the effect of mixed-stock fishery outcome uncertainty, while reducing the effect of single-stock outcome uncertainty. The opposite pattern occurred when single-stock fishery allocations were increased. Since qualitative patterns were otherwise similar, these results are not shown.

We set the minimum temporal autocorrelation $\tau$ value at zero and the maximum at the largest estimated value from a study of Alaskan sockeye salmon [@Peterman2003]. Spawner observation error was bounded by zero (i.e. all spawners were enumerated perfectly) and one [@Holt2018]. To evaluate the sensitivity of fishery-specific outcome uncertainty we set the lower value for $\sigma_{out}$ at zero (i.e. no deviations between target and realized catch) and the maximum value at 0.15, an arbitrary value resulting in ~20% of harvest rate deviations exceeding the maxmimum deviation observed among all Fraser River sockeye salmon management units between 2006 and 2017. Conversely, the reference $\sigma_{out}$ (0.07) results in ~0.2% of deviations exceeding the maximum observed. We applied the same minimum and maximum values to both single- and mixed-stock fisheries, but did so independently. Finally, to evaluate interannual variability in age-at-maturity and en-route mortality we applied scalars to $\gamma$ and $\sigma_{mort}$ consistent with stock-specific differences (i.e. were within on standard deviation of observed values; Table S2.1). 

```{r tableS2, results="asis"}
pars <- c("$\\tau$", "$\\sigma_{obs}$", "$\\sigma_{out}$",
          "$\\gamma$","$\\sigma_{mort}$") 
refVals <- c(0.2,
             0.2,
             0.07,
             paste("stock-specific (range ", min(cuPar$tauCycAge), "-",
                max(cuPar$tauCycAge), ")", sep = ""),
             paste("stock-specific (range ", round(min(cuPar$sdDBE), 2), "-",
                round(max(cuPar$sdDBE), 2), ")", sep = ""))
minVals <- c(0, 0, 0, "0.5 * ref. $\\gamma$", "0.75 * ref. $\\sigma_{mort}$")
maxVals <- c(0.72, 1, 0.15, "1.25 * ref. $\\gamma$", 
             "1.25 * ref. $\\sigma_{mort}$")

sensPars <- data.frame(
  Parameter = pars,
  Reference = refVals,
  Minimum = minVals,
  Maximum = maxVals
)

csas_table(sensPars,
  caption = "Table S3.1. Parameter values for components of operating model and management procedure that were adjusted in sensitivity analyses.",
  font_size = 12,
  col_names = c("Parameter", "Ref. Value", "Min. Value", "Max. Value")
)
```


```{r generateData, include=FALSE}
vars <- c("medRecRY", "medSpawners", "ppnCULower", "medCatch", "stabilityCatch",
          "medER")

agDotPlotList <- lapply(seq_along(vars), function(x) {
  dum <- plotDat %>% 
    filter(var == vars[x],
           !scen == "genericRetro") 
  dumRef <- plotDat %>% 
    filter(var == vars[x],
           scen == "genericRetro")
  
  p <- ggplot(dum, aes(x = scen, y = avg, ymin = lowQ, ymax = highQ,
                       fill = om)) +
    labs(x = "", y = unique(dum$labelledVar)) +
    geom_pointrange(shape = 21, fatten = 4, size = 1,
                    position = position_dodge(width = 0.65)) +
    geom_hline(dumRef, mapping = aes(yintercept = avg), linetype = 1) +
    geom_hline(dumRef, mapping = aes(yintercept = lowQ), linetype = 2, 
               size = 0.5) +
    geom_hline(dumRef, mapping = aes(yintercept = highQ), linetype = 2, 
               size = 0.5) +
    scale_x_discrete(labels = c("ageTau" = "Mat.\nAge",
                                "mixOU" = "Mixed\nOU",
                                "singOU" = "Single\nOU",
                                "rho" = "Temp.\nAuto.",
                                "enRouteSig" = "Mig.\nMort.",
                                "obsSig" = "Obs.\nSpawn.")) +
    scale_fill_discrete(name = "Sensitivity\nAnalysis",
                      labels = c("Lower\nBound", "Upper\nBound"))
  if (unique(dum$pmClass) == "catch") {
    p <- p +
      theme_sleekX(position = "bottom", axisSize = 10, legendSize = 1.05)
  } else {
    p <- p +
      theme_sleekX(position = "top", axisSize = 10, legendSize = 1.05)
  }
  return(p)
})
```

The effects of our sensitivity analyses differed among parameters and performance metrics. For example, greater temporal autocorrelation in recruitment deviations led to declines in recruitment, escapement, the proportion of stocks above their biological benchmark, and catch (Fig. S3.1). Such patterns are likely due to temporal autocorrelation weakening compensatory biological and management processes. Increasing or decreasing the observation error associated with estimates of spawner abundance had negligible impacts on all performance metrics (Fig. S3.1). Increasing outcome uncertainty, particularly within mixed-stock fisheries had the strongest impact, with greater deviations between realized and target catch resulting in reduced performance across all conservation and catch metrics (Fig. S3.1). Such patterns are consistent with evidence that outcome uncertainty can negatively affect conservation and harvest objectives [@Holt2006]. Single-stock outcome uncertainty exhibited a similar pattern; however effect was weaker because single-stock exploitation rates were, on average, lower, reducing the risk of overharvest (Fig. S3.1). Changes in interannual variability in maturation age and en route mortality rates had relatively minor effects on all performance metrics (Fig. S3.1). 

Regardless of the performance metric or focal parameter, however, 90% quantile intervals for each sensitivity scenario overlapped the reference opearting model (Fig. S3.1). Since this pattern was stable when allocations were fully single- or fully mixed-stock (not shown), the conclusions presented in the main text are unlikely to be biased by the magnitude of stochastic parameters.

```{r sensPlot, warnings=FALSE, messages=FALSE, fig.cap="Figure S3.1 Sensitivity of conservation- and catch-based performance metrics to stochastic parameters and temporal autocorrelation. All scenarios assume a 50% of the total allowable catch was allocated to each fishery. Horizontal lines represent the median (solid) estimate and 90th percentile intervals (dashed) from the reference operating model. Points represent medians and whiskers represent 90th percentile intervals among Monte Carlo trials."}
panelPlot <- ggpubr::ggarrange(agDotPlotList[[1]], agDotPlotList[[2]],
                               agDotPlotList[[3]], agDotPlotList[[4]],
                               agDotPlotList[[5]], 
                               # agDotPlotList[[6]],
                               ncol = 3, nrow = 2, common.legend = TRUE,
                               legend = "right",
                               heights = c(0.85, 1))
ggpubr::annotate_figure(panelPlot,
                        bottom = ggpubr::text_grob("Proportion Mixed-Stock TAC",
                                                   size = 12, vjust = -1))
```

_Literature Cited_

